Stability And Performance Of Virtual Aggregations Of Prosumers Through Diversification In The Smart Grid

### 2015-07-31 Article.tex
update

\begin{equation}
\delta_{S}(i) \geq 0 \Leftrightarrow P_{S+\{i\}}^{CRCT \star} \geq P_{S}^{CRCT \star} \left( \dfrac{|S|+1}{|S|} \right)^{\alpha}
\label{eq:marginal_benefit}
\end{equation}

@@

Figure \ref{fig:mean_approx} shows how $ \alpha^{\star} $ and the utility function evolves according to the mean size of the coalitions $ \bar{N} $. These nice curves are of course only valid in the simplified example considered here, but they will provide some guidance when using real data.

@@

%Clearly, if $ \alpha = 0 $, whatever the size of the coalition, additional agents are added as long as they increase the contract value. Values of $\alpha $ greater than zero implies that additional agents must improve the contract value by a certain coefficient that decreases and converges to one as the size of the coalition is growing. For instance, if $\alpha = 1$ and $ |S| = 1 $, an additional agent must first double the contract value to be included, the next agent will then have to increase it by a factor of $ 1.5 $, and so on... Obviously, $ \alpha $ impacts directly the sizes of the coalitions formed. In the following, we consider the case where $ \alpha = 1 $.

@@

\begin{equation}
\label{epsilon_star}
\epsilon^{\star} = min_{ \epsilon \in [0,1]} \left\{ \epsilon\ s.t.\ |\Theta_{k}(G_{2}^{\epsilon})| \geq N_{COAL} \right\}
\end{equation}

Where $ G_{2}^{\epsilon} $ is the de-correlation graph $ G_{2} $ filtered by $ \epsilon $, and $ \Theta_{k}(G) $ is the set of non overlapping cliques of size k in a given graph G. In other words we select $ \epsilon^{\star} $ as the smallest threshold possible such that the filtered de-correlation graph contains at least $ N_{COAL} $ non overlapping cliques of size k. The existence of $ \epsilon^{\star} $  as defined in equation  \ref{epsilon_star} is not guaranteed. The users has indeed to provide consistent values of $ N_{COAL} $ or k compared to the size of the agent population $ \mathcal{A} $.

@@

Directly mapping cliques to coalitions by this de-correlation oriented approach is thus not sufficient. It is indeed possible that adding agents to these cliques has the combined effect of increasing the expected production while decreasing its stability. The question revolves around measuring the benefits of this production surplus compared to the disadvantage of having coalition with high volatility. This can be quantified by the marginal benefit of equation \ref{eq:marginal_benefit}.

>>>>

\begin{equation}
\delta_{S}(i) \geq 0 \ \ \ \Leftrightarrow \ \ \ P_{S+\{i\}}^{CRCT \star} \geq P_{S}^{CRCT \star} \left( \dfrac{|S|+1}{|S|} \right)^{\alpha}
\label{eq:marginal_benefit}
\end{equation}

@@

Figure \ref{fig:mean_approx} shows how $ \alpha^{\star} $ and the utility function evolves according to the mean size of the coalitions $ \bar{N} $. These curves are only valid in the simplified Gaussian example considered here. Nonetheless, they will provide some guidance when using real data.

@@

@@

\begin{equation}
\label{epsilon_star}
\epsilon^{\star} = min_{ \epsilon \in [0,1]} \left\{ \epsilon\ s.t.\ |\Theta_{k}(G_{2}^{\epsilon})| \geq N_{COAL} \right\}
\end{equation} 
where $ G_{2}^{\epsilon} $ is the de-correlation graph $ G_{2} $ filtered by $ \epsilon $, and $ \Theta_{k}(G) $ is the set of non overlapping cliques of size k in a given graph G. In other words we select $ \epsilon^{\star} $ as the smallest threshold possible such that the filtered de-correlation graph contains at least $ N_{COAL} $ non overlapping cliques of size k. The existence of $ \epsilon^{\star} $  as defined in equation  \ref{epsilon_star} is not guaranteed. The users has indeed to provide consistent values of $ N_{COAL} $ or k compared to the size of the agent population $ \mathcal{A} $.

@@

Directly mapping cliques to coalitions by this de-correlation oriented approach is thus not sufficient. It is indeed possible that adding agents to these cliques has the combined effect of increasing the expected production while decreasing its stability. The question revolves around measuring the benefits of this production surplus compared to the disadvantage of having coalition with high volatility. This can be quantified by the marginal benefit in equation \ref{eq:marginal_benefit}.
